---
title: "Worksheet#4"
author: "Gabriel Leornas BSIT-2A"
date: "2022-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***1. The table below shows the data about shoe size and height. Create a data frame..***

**library(dplyr)**
**library(readr)**
**library(data.table)**


**a. Describe the data.**

```{r, num1a}
Shoesize <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,
              7.5,10.5,8.5,12.0,10.5,
              13.0,11.5,8.5,5.0,10.0,
              6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)
Height <- c(66.0,68.0,64.5,65.0,70.0,
            64.0,70.0,71.0,72.0,64.0,
            74.5,67.0,71.0,71.0,77.0,72.0,
            59.0,62.0,72.0,66.0,64.0,67.0,73.0,
            69.0,72.0,70.0,69.0,70)
Gender <- c("F","F","F","F","M","F","M","F","M",
             "M","M","F","M","M","M","M","F","F",
            "M","F","M","M","M","F","M","M","M","M")
 df <- data.frame(Shoesize,Height,Gender)
 df
```
 
***Answer: The output will show a data base on what we put on each rows within the dataframe***
 
**b. Find the mean of shoe size and height of the respondents.**
**Copy the codes and results.**

+
***Male***

```{}
summary(df)
```

+


**c. Is there a relationship between shoe size and height? Why?**

**Yes, The Higher the value of height, the greater value of the Shoesize.**


***2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.***

```{}
Months <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August",
"July","December","August","August","September","November","February","April")

factor_Months <- factor(Months)
factor_MonthsMonths_Vector <- c("March","April","January","November","January",
            "September","October","September","November","August",
            "January","November","November","February","May","August",
            "July","December","August","August","September","November","February","April")
Factor_Month_Vector <- factor(Months_Vector)
Factor_Month_Vector
```

***3. Then check the summary() of the Months_Vector_vector and Factor_Month_Vector_vector.***
**Interpret the results of both vectors. Are they both equally useful in this case?**

```{}
summary(Months)
summary(factor_Months)
```

**Answer: For me Yes, as for the months_vector it shows the number of months**


***4. Create a vector and factor for the table below.***

```{}
factorData <- data.frame(
 Direction = c("East","West","North"),
 Frequency = c(1,4,3)
)
factorData
newOrderData <- factor(factorData,levels = c("East","West","North"))
print(newOrderData)
```

***5. Enter the data below in Excel with file name = import_march.csv***

**a. Import the excel file into the Environment Pane using read.table() function.**
```{}
library(readxl)
import_march <- read_excel("Worksheet#4/import_march.xlsx")
View(import_march)
```
**b. View the dataset. Write the code and its result.**
```{}
Students `Strategy 1` `Strategy 2` `Strategy 3`
  <chr>           <dbl>        <dbl>        <dbl>
1 Male                8           10            8
2 NA                  4            8            6
3 NA                  0            6            4
4 Female             14            4           15
5 NA                 10            2           12
6 NA                  6            0            9
```