---
title: "Worksheet#5"
author: "Gabriel Leornas BSIT-2A"
date: "2022-11-22"
output: pdf_document
---
#Gabby

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.**

***a. Plot the data using a bar graph. Write the codes and copy the result.***

```{r, num1a}
x2019_2020 <- c(80,75,70,60)
numb_1a <- barplot(x2019_2020)
numb_1a
```

***b. Using the same table, label the barchart with***
***Title = ” Enrollment of BS Computer Science***
***horizontal axis = “Curriculum Year” and***
***vertical axis = “number of students”***

```{r, num_1b}
course <- c("1st","2nd","3rd","4th")
numb_1b <- barplot(x2019_2020,
        main = "Enrollment of BS Computer Science",
        xlab = "Curriculum Year", names.arg = course)
```

**2. The monthly income of De Jesus family was spent on the following:**
**60% on Food, 10% on electricity, 5% for savings, and**
**25% for other miscellaneous expenses.**


***a. Create a table for the above scenario.***
***Write the codes and its result.***

```{r, num2a}
num2a <- data.frame(
  expenses = c("Food", "Electricity", "Savings", "Miscllaneous"),
  Percentage = c(60,10,5,25)
)
num2a
expenses <- c(60,10,5,25)
barplot(expenses,names.arg = c("Food", "Electricity", "Savings", "Miscllaneous"))
```

***b. Plot the data using a pie chart. Add labels, colors and legend.***
***Write the codes and its result.***

```{r, num2b}
pie(expenses)
numb2b <- pie(expenses,
    col = rainbow(length(expenses)),
    labels = c(60,10,5,25))
```

```{r, num2b1}
ex_labels <- round(expenses/sum(expenses) * 100, 1)
ex_labels <- paste(ex_labels,"%",sep = "")
pie(expenses, main = "Expenses",col=rainbow(length(expenses)),labels = ex_labels,cex=0.8)
legend(1, c("Food", "Electricity", "Savings", "Miscllaneous"),
           cex = 0.8,fill = rainbow((length(expenses))))
```

**3. Open the mtcars dataset.**

```{r, num3}
data("mtcars")
numb3 <- mtcars$mpg
```

***a. Create a simple histogram specifically for mpg (miles per gallon) variable.***
***Use $ to select the mpg only. Write the codes and its result.***

```{r, num3a}
numb3a <-hist(numb3, xlab="Miles Per Gallon",
              main="Histogram of mpg")
```

***b. Colored histogram with different number of bins.***

```{r,  num3b}
numb3b <-hist(numb3, breaks=12, col="red", xlab="Miles Per Gallon",
              main="Histogram of mpg")
```

***Note: breaks= controls the number of bins***

***c. Add a Normal Curve***

```{r, num3c}
numb3c <-hist(numb3, breaks=12, col="red", xlab="Miles Per Gallon",
        main="Histogram with Normal Curve")
xfit<-seq(min(numb3),max(numb3),length=40)
yfit<-dnorm(xfit,mean=mean(numb3),sd=sd(numb3))
yfit <- yfit*diff(numb3c$mids[1:2])*length(numb3)
lines(xfit, yfit, col="blue", lwd=2)
```
***Copy the result.***

**4. Open the iris dataset. Create a subset for each species.**

***a. Write the codes and its result.***

```{r, num4a}
data("iris")
set <- subset(iris, Species == "setosa")
ver <- subset(iris, Species == "versicolor")
vir <- subset(iris, Species == "virginica")
```

***b. Get the mean for every characteristics of each species using colMeans().***
***Write the codes and its result.***

```{r, num4b}
set <- subset(iris, Species == "setosa")
setosa <- colMeans(set[sapply(set,is.numeric)])
setosa
ver <- subset(iris, Species == "versicolor")
versicolor <- colMeans(ver[sapply(ver,is.numeric)])
versicolor
vir <- subset(iris, Species == "virginica")
virginica <- colMeans(vir[sapply(vir,is.numeric)])
virginica
```

*Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])*
***c. Combine all species by using rbind()***
***The table should be look like this:***

```{r, num4c}
trans3 <- rbind(setosa,
                versicolor,
                virginica)
trans3
```

***d. From the data in 4-c: Create the barplot().***
***Write the codes and its result.***
***The barplot should be like this.***

```{r, num4d}
barplot(trans3, beside = TRUE,
        main = "Iris Mean",
        xlab = "Characteristics",
        ylab = "Mean Scores",
        col = c("red","green","blue"))
```


***Figure 1: Iris Data using Barplot***